Molecular dynamics simulation of synchronization in driven particles

### 2021-02-19 manuscript/manuscript_ajp_2020.tex
found a mistake in the code

We confine the particles using a position dependent 
potential energy function, called a landscape or substrate.
 %The landscape potential energy $U(\vec{r})$ is static 
 %with fixed minima and maxima
 %that are periodic or quasi-periodic,
 %as described in Sec.~\ref{sec:results}.
% 
The landscape is modulated in the y-direction
with the periodic function 
%% %that used in Sec.~\ref{sec:one}
% where 
 \begin{equation}
   U(y) = U_0 \cos{(N_p \pi y / L)}
     \label{eq:ysubstrate}
\end{equation}
 where $N_p$ are the number of periods,
 % $L$ is the period length,
 and $U_0$ is an adjustable parameter
 to set the depth of the minima
 with simulation units of energy $E_0 = 1$. 
 %We define the substrate strength to be
 %the maximum force the substrate can exert on a particle 
 %
 We plot this function in 
 Fig.~\ref{fig:landscape0}
 for $N_p = 3$. %to illustrate the features of
 In Fig.~\ref{fig:landscape0}(a) we show 
 the $x-y$ plane with a contour plot of $U(y)$ %Eq.~\ref{eq:ysubstrate}
 to illustrate
 the 2D potential energy landscape,
 where 
 the maxima are colored red and the minima colored blue.
 The confining force on a particle $i$
 %arises from a potential function 
 %creating a landscape of potential minima and maxima
 %that modify the force on a particle as a function of position
 is calculated as 
 $\vec{F}^{l}_i(\vec{r}_i) = -\nabla U_l(\vec{r}_i)$.
 In Fig.~\ref{fig:landscape0}(b) we plot the function
 $U(y)$ to illustrate how the magnitude
 $\vec{F}^{l}_i$ is calculated from particle position $y_i$.  
 %in the $y-$direction.

@@

\begin{table}[h!]
\centering
\caption{Simulation parameters and units and comparable
  experimental values~\cite{Juniper2015}.
  Blanks %in the experimental parameters
  indicate
  units, rather than parameters that
  are not easily represented by a single value.}
%{\it might be more appropriate to match Juniper parameters more precisely given our focus...}}
\begin{ruledtabular}
\begin{tabular}{c c c } %p{5cm}}
Quantity & Simulation Unit & Experimental value\\
\hline
length &  $a_0 = 1$ & $ a_0 \sim 1.5 \mu m$\\
energy & $E_0 = 1$ & \\ %$ < E_0 <$ \\
%electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
%energy & $E_0 = q^2{Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
%dimensionless interaction strength & $q$ \\
%effective colloidal charge & $Z^*$ \\
%solvent dielectric constant & $\epsilon \epsilon_0$\\
force & $F_0 = E_0 / a_0$ & \\ %$<F_0<$\\
time &  $ \tau = \eta a_0 / F_0 $ \\ %& $ < \tau <$\\
velocity &  $ a_0 / \tau $ &  $v \sim 5 \mu m/s $\\
driving period & $T = 100 \tau$ & $T \sim 1.3$ s \\
viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $\eta \sim 10^{-3}$ Pa-s \\
%juniper uses water–ethanol mixture
substrate period & $\lambda = 1.825 a_0$ & $\lambda = 3.5 \mu m$ \\
substrate amplitude & $U_0 = 0.058 E_0$ & $U_0 = 75 k_B T \sim 2 J$ \\
%A_p = 0.1 = N_p pi U_0/L.  this is how calculated U_0
temperature & $T_0 = 0$ \footnote{to learn more about the effects
  of temperature on this simulation
  see Ex.~\ref{ex:brownian} where we study the limit
  $U_0 \sim k_B T$.} & $T \sim 300K $ \\

@@

Here we drive 
a single particle %on this landscape
%responds to the applied driving force
%by moving
across the landscape %maxima
to characterize its motion.
%synchronized with 
%the period of $F^D(t)$.
%applied driving force.
%along the y-direction
%({\it redundant, just refer back to eq. in Model?})
%and $V_{0y}=0.2$.
%This is illustrated in Fig.~\ref{fig:1}(a) where
%the red (blue) regions show local maxima (minima).
%
The numerical implementation of the landscape 
is calculated with Eq.~\ref{eq:ysubstrate} as 
\begin{equation}
  \label{eq:force}
  F^l_y(y) = -A_{p} \sin{(N_p \pi y / L)} 
\end{equation}
where the force is scaled with parameter $A_{p} = N_p \pi U_0/L$.
In this section we fix the landscape parameters
to $A_{p} = 0.1 F_0$ %force units
with $N_p=20$ minima %in the landscape
corresponding to a spatial period $\lambda = 1.825 a_0$.

%In Fig.~\ref{fig:0} 
The driven particle %adjusts
moves across %its motion to traverse
the periodic landscape with the same rhythm as 
the applied time-dependent force $F^D(t)$.
When $F^D(t) > A_p$, a particle can 
overcome the barrier height of the landscape,
and 
the particle hops between minima in the energy landscape.
%
In Fig.~\ref{fig:0}(a)
we plot $F^D(t)$ %defined in Eq.~\ref{eq:drive}.
as a function of time with
%The time independent
constants $F^{dc}=0.1$, 
$F^{ac}=0.05$ and $f=0.01$ cycles per time unit $\tau$.
The temporal period of the driving force is
$T = 1/f = 100 \tau$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%RAMP
%To avoid transient oscillations at early times, the dc driving force is initially zero and slowly increased %$F^{dc}$. at a rate of $\Delta F^{dc} = 0.01$ every $\Delta t = 4$ time units  to the constant value $F^{dc}=0.1$. In Fig.~\ref{fig:0}(a) we plot $F^{dc}$ in blue to show the increase in  $F^{dc}$ for the first $40$ time units In orange we show  the combined ac and dc drive $F^D(t)$ when the magnitude of the ac applied force is initially zero.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%since $\sin{(0)}=0$.
We mark the maxima of $F^{ac}(t)$
with the
vertical dashed lines %in panels (a) and (b)
-- i.e. $\sin{(\omega t)} = 1$.
%
%
%with the initial driving force at is minimum value 
%$F^D(0) = F^{dc}$. 
%
In Fig.~\ref{fig:0}(b) 
we show the $y-$position of the particle
as a function of time.
We 
normalize $y$ by $\lambda$ %, the spatial period of the potential
to show  particle motion between substrate minima.  
The initial particle position is $y = 0 $. %1 a_0$,
%where the $F^l$ is negative.
%JUST BECAUSE
%causing the particle to move to
%a landscape minima at the start of the simulation.
As the driving force increases,
%the effects of the landscape become less obvious,
the motion of the particle
synchronizes with the driving period $T$.
We measure 
average particle velocity $\langle{v}_y\rangle$
as the displacement %$\Delta y = y(t_0+T) - y(t_0)$
over the period of the driving force.
The particle moves
in the positive y-direction
through $\Delta y = 2 \lambda$ over the time period $T$,
with 
the average velocity 
$\langle {v}_y \rangle= 2 \lambda f$. % where $T = 1/f$.
The horizontal dashed lines
coincide with the condition the particle is at a substrate minima
where substrate force  $F^l = -A_p$,  
i.e. $\sin{(\pi y / \lambda)} = 1$.
%or $\pi y / \lambda = m \pi/2$, where $m = 1, 5, 7$, {\it etc.}
%Once the particle motion
%coincides with the applied drive,
%indicating synchronization,
The particle synchronizes its motion such that the 
driving force is maximum when the landscape 
force is minimum,
as indicated %with the coincidence of 
with the intersection of
vertical and horizontal lines.  
%i.e. the particle position $y/\lambda$.  
The slope of $y/\lambda$
is proportional to the net force on the particle.
This can be seen in 
Fig.~\ref{fig:0} %we demonstrate this relationship,
where local extrema appear in $y/\lambda$
when $F_{D}(t) \approx 0 $. 
\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{single_particle.pdf}
\caption{(a) The applied driving force $F^D(t)$. % (Eq.~\ref{eq:drive}).
  %where the parameter $F^{dc}$ (blue) is slowly increased from zero %to a constant value %as described in the text.
  (b) 
  The $y-$position of the driven particle
  %of a single driven particle
  normalized by the period of the substrate $\lambda$.
  %as a function of time
  }
\label{fig:0}
\end{figure}
\end{center}

The competition between the driving force and landscape potential
can produce a variety of hopping patterns in the particle motion. 
%In Fig.~\ref{fig:0}
%reaching a minimum position
%of $y/\lambda = 1$
%over the total period $T = 100$.
%In Fig. ~\ref{fig:0}
%the average displacement during one time period is a single wavelength
%of the substrate $y(t_0+T) - y(t_0) = \lambda$.
%single dc case with figure
%dc_current 0.01
%ac_current 0.05
%ac_frequency 0.01
%fp_y 0.1
%
The relative values of $F^{ac}$, $F^{dc}$ and $A_p$
control the rate and distance a  particle moves 
forward and backward in the landscape.

  It is useful to compare
  mode-locked quantities %periodic signals
  in a two dimensional phase plot.
  In a non-driven system, an appropriate
  phase space is particle velocity $v_y$ versus position $y$.  
  In a system driven parallel to the $y-$direction,
  %the particle velocity and position increase
  %in time. % due to $F^{dc}$.
  %Since a system does not form
  %a closed loop in
  %$v_y$ vs $y$ space,
  we define phase variables 
  to account for the net increase in velocity
  and position.
  The phase position is
  defined as 
  %within the substrate period as 
  %We define a phase variable 
  \begin{equation}
    %(y mod \lambda) / \lambda
    \phi(t) = 2\pi(y(t)-\langle v_y \rangle t)/\lambda
  \end{equation}
  centered about the average particle velocity $\langle v_y \rangle$
  and normalized by the substrate period $\lambda$ \cite{Juniper2015}.
  We plot this phase
  versus the phase velocity 
  \begin{equation}
    %(y mod \lambda) / \lambda
    \dot{\phi}(t) = 2\pi(v_y(t)-\langle v_y \rangle /\lambda.
  \end{equation}
  %Juniper %REF 53
  %and easily generated with a computer code 
  %or oscilloscope \cite{Tong1997}.
  When velocity
  is mode-locked to %repeat periodically
  a spatial location
  a closed loop appears in  
  phase space. % showing the relationship
  %between two periodic functions
  The pattern is determined by the mode,
  or frequency ratio,
  so a 1:1 mode appears as a circle or oval.
  Nodes appear in the oval 
  for higher modes,
  sometimes forming figure-eights
  or other recognizable patterns.
  A system that is not fully phase locked
  will apppear as an unclosed loop.
  Such quasiperiodic systems are
  not fully synchronized.
  %and the shifts in phase space represent
  %small changes in system behavior.
  With a long simulation time,
  a quasiperiodic phase diagram
  fills the plotting region due to the gradual shift
  in the velocity-position relationship.
  %with a frequency generator,
  %where two combined frequencies at perpendicular orientations
  %\footnote{The term phase
  %has two scientific meanings:  
  %oscillation phase $\phi_0$ is the constant of the argument
  %in a periodic function
  %$\sin{(\omega t + \phi_0)}$ and phase space is
  %used to characterize oscillating systems with
  %parametric plots.}.

  In Fig.~\ref{fig:phase}
  we plot $\dot{\phi}(t)$ versus $\phi(t)$
  for increasing substrate amplitude $A_p$.
  We fix the driving force with parameters
  $F^{dc} = 0.1$ and frequency $f = 0.01$ and $F^{ac} = 0.2$.
  In Fig.~\ref{fig:phase}(a)
  there is no substrate ($A_p = 0.0$)
  and the phase plot is a closed oval
  centered at
  $(\phi,\dot{\phi})=(10,0)$
  with a semimajor axis of $\Delta \phi = 20$ %ANALYTIC
  and semiminor axis of $\Delta \dot{\phi} = 2\pi/\lambda v_{max}$.
  [insert analysis.]
  As the force from the substrate
  increases,
  nodes form in the phase diagram
  and the motion becomes quasiperiodic
  so the loops in phase space do not fully overlap.
  In Fig.~\ref{fig:phase}(b)
  $A_p = 0.05$
  the spatial properties are similar to
  those in $A_p = 0.0$
  with 
  $(\phi,\dot{\phi})=(10,0)$
  with a semimajor axis of $\Delta \phi = 20$.
  The dynamical properties
  are asymmetric,
  with three nodes in the positive $\dot{\phi}$ values.
  The thickening of the line
  indicates the system is not fully synchronized.
  [insert analysis.]
  As the substrate
  force becomes larger,
  $\phi$ shifts to lower values
  and $\dot{\phi}$ to positive values,
  indicating
  the particle can only move 
  backward over a short distance.
  In Fig.~\ref{fig:phase}(c)
  $A_p = 0.1$
  the phase properties are similar to
  those in $A_p = 0.05$,
  the three nodes have 
  increased asymmetry in both phase variables 
  $(\phi,\dot{\phi})$.
  The nodes deepen,
  indicating [insert analysis.].
  In Fig.~\ref{fig:phase}(d)
  $A_p = 0.2$
  the pattern shifts
  to two nodes,
  [indicating change analysis].
  In Fig.~\ref{fig:phase}(e)
  $A_p = 0.25$
  the system returns to a nodeless
  orbit,
  shaped like a triangle [because why?]
  In Fig.~\ref{fig:phase}(f)
  $A_p = 0.3$
  the particle is trapped between substrate minima,
  and traces out a small unclosed
  orbit in phase space [because...]
  The phase velocity is near zero
  throughout the motion -
  [comment on initial conditions]
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{phase.pdf}
      \caption{
        Phase plot of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0}.  $F^{ac} = 0.2$ and $A_p = $ (a) $0.0$, (b) $0.05$, (c) $0.1$, (d) $0.2$, (e) $0.25$ and (f) $0.3$.
      }
      \label{fig:phase}
    \end{figure}
  \end{center}

@@

  %Consider a non-zero temperature in the simulation.
  %in which particles will collide with invisible particles
  %making up the suspending fluid.
  In molecular dynamics simulations
  it is common to treat the 
  invisible fluid particles as a continuous substance
  to reduce computational expense.
  Temperature effects
  can be modeled by applying randomized forces $f^T$
  to the visible particles.
  %\footnote{%In our simulations %np.random.normal
  We use the normal distristribution from the NumPy random module
  to generate a series of $f^T_n$ values for
  each integer timestep $n$ \cite{numpy}.
  A normalized random distribution of forces
  causes fluctuations in %particles to emulate Brownian
  motion 
  equally in all
  directions such that the force $f^T$
  averaged over a finite time interval
  is zero.  In one dimension this is expressed as 
  \begin{equation}
    \langle f^T(t) \rangle = \frac{1}{N} \sum_n^N f^T_n = 0
  \end{equation}
  %where $n$ is an integer indicating
  %discrete simulation timesteps
  such that $t = N \Delta t$.
  Random normal distributions are not correlated 
  over the independent variable,
  for the independent variable to be time
  \begin{equation}
  \langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)
  \end{equation}
  for times $t$ and $\tau$,
  where $\delta(t-\tau)$ is the Dirac-delta function.
  Here the scaling factor energy of 
  $k_B T$ is
  derived from the Boltzmann constant $k_B$
  and temperature $T$ \cite{Allen2017}.
  A particle
  with sufficient energy $k_b T_{min}$ may 
  hop over landscape
  barriers.
  % (a) 
  In our simulations,
  we define temperature as 
  $k_b T/E_0 \rightarrow T$
  with constants set to unity
  to
  %In these units
  compare directly with force. 
  %in order to estimate the degree of random fluctuation.

>>>>

We confine the particles using a position dependent 
potential energy function, called a landscape or substrate.
 %The landscape potential energy $U(\vec{r})$ is static 
 %with fixed minima and maxima
 %that are periodic or quasi-periodic,
 %as described in Sec.~\ref{sec:results}.
% 
The landscape is modulated in the y-direction
with the periodic function 
%% %that used in Sec.~\ref{sec:one}
% where 
 \begin{equation}
   U(y) = U_0 \cos{(2 \pi y / \lambda)}
     \label{eq:ysubstrate}
\end{equation}
 where $\lambda=L/N_p$ with $N_p$ are the number of periods,
 % $L$ is the period length,
 and $U_0$ is an adjustable parameter
 to set the depth of the minima
 with simulation units of energy $E_0$. 
 %We define the substrate strength to be
 %the maximum force the substrate can exert on a particle 
 %
 We plot this function in 
 Fig.~\ref{fig:landscape0}
 for $N_p = 3$. %to illustrate the features of
 In Fig.~\ref{fig:landscape0}(a) we show 
 the $x-y$ plane with a contour plot of $U(y)$ %Eq.~\ref{eq:ysubstrate}
 to illustrate
 the 2D potential energy landscape,
 where 
 the maxima are colored red and the minima colored blue.
 The confining force on a particle $i$
 %arises from a potential function 
 %creating a landscape of potential minima and maxima
 %that modify the force on a particle as a function of position
 is calculated as 
 $\vec{F}^{l}_i(\vec{r}_i) = -\nabla U_l(\vec{r}_i)$.
 In Fig.~\ref{fig:landscape0}(b) we plot the function
 $U(y)$ to illustrate how the magnitude
 $\vec{F}^{l}_i$ is calculated from particle position $y_i$.  
 %in the $y-$direction.

@@

\begin{table}[h!]
\centering
\caption{Simulation parameters and units with comparable
  experimental values~\cite{Juniper2015}.}
  %Blanks indicate you are a moron
  %units, rather than parameters that
  %are not easily represented by a single value.}
%{\it might be more appropriate to match Juniper parameters more precisely given our focus...}}
\begin{ruledtabular}
\begin{tabular}{c c c } %p{5cm}}
Quantity & Simulation Unit & Experimental value\\
\hline
length &  $a_0 = 1$ & $ a_0 \sim 1.5 \mu m$\\
energy & $E_0 = 1$ & \\ %$ < E_0 <$ \\
%electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
%energy & $E_0 = q^2{Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
%dimensionless interaction strength & $q$ \\
%effective colloidal charge & $Z^*$ \\
%solvent dielectric constant & $\epsilon \epsilon_0$\\
force & $F_0 = E_0 / a_0$ & \\ %$<F_0<$\\
time &  $ \tau = \eta a_0 / F_0 $ \\ %& $ < \tau <$\\
velocity &  $ a_0 / \tau $ &  $v \sim 5 \mu m/s $\\
driving period & $T = 100 \tau$ & $T \sim 1.3$ s \\ %frequency 0.75 Hz
viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $\eta \sim 10^{-3}$ Pa-s \\
%juniper uses water–ethanol mixture
substrate period & $\lambda = 1.825 a_0$ & $\lambda = 3.5 \mu m$ \\
substrate amplitude & $U_0 = 0.058 E_0$ & $U_0 = 25 k_B T \sim 2 J$ \\
%they have 75 k_B T as the bottom of -U_0
%A_p = 0.1 = N_p pi U_0/L.  this is how calculated U_0
temperature & $T_0 = 0$ \footnote{to learn more about the effects
  of temperature on this simulation
  see Ex.~\ref{ex:brownian} where we study the limit
  $U_0 \sim k_B T$.} & $T \sim 300K $ \\

@@

Here we drive 
a single particle %on this landscape
%responds to the applied driving force
%by moving
across the landscape %maxima
to characterize its motion.
%synchronized with 
%the period of $F^D(t)$.
%applied driving force.
%along the y-direction
%({\it redundant, just refer back to eq. in Model?})
%and $V_{0y}=0.2$.
%This is illustrated in Fig.~\ref{fig:1}(a) where
%the red (blue) regions show local maxima (minima).
%
The numerical implementation of the landscape 
is calculated with Eq.~\ref{eq:ysubstrate} as 
\begin{equation}
  \label{eq:force}
  F^l_y(y) = -A_{p} \sin{(2 \pi y / \lambda)} 
\end{equation}
where the force is scaled with parameter $A_{p} = 2\pi U_0/\lambda$.
In this section we fix the landscape parameters
to $A_{p} = 0.1 F_0$ %force units
with $N_p=20$ minima %in the landscape
corresponding to a spatial period $\lambda = 1.825 a_0$.
The competition between the driving force and landscape potential
can produce a variety of hopping patterns in the particle motion. 
%In Fig.~\ref{fig:0}
%reaching a minimum position
%of $y/\lambda = 1$
%over the total period $T = 100$.
%In Fig. ~\ref{fig:0}
%the average displacement during one time period is a single wavelength
%of the substrate $y(t_0+T) - y(t_0) = \lambda$.
%single dc case with figure
%dc_current 0.01
%ac_current 0.05
%ac_frequency 0.01
%fp_y 0.1
%
The relative values of $F^{ac}$, $F^{dc}$ and $A_p$
control the rate and distance a  particle moves 
forward and backward in the landscape.
[edit and move:] The addition of an oscillating force
can lead to interference effects
that create stepped force-velocity curves.
Useful model - essentially an overdamped driven pendulum -
under certain parameters.
The steps occur
due to the phase locking between lattice substrate
and applied driving force.
Step widths depend on AC drive.
Discrete modes.
%Shapiro steps wash out to sloped regions at
%high vortex numbers,
%so what is the analog in my system?
%need to sweep through more parameters to find and report the flat regions
%not fully phase locked.

%In Fig.~\ref{fig:0} 
The driven particle %adjusts
moves across %its motion to traverse
the periodic landscape with the same rhythm as 
the applied time-dependent force $F^D(t)$.
When $F^D(t) > A_p$, a particle can 
overcome the barrier height of the landscape,
and 
the particle hops between minima in the energy landscape.
%
In Fig.~\ref{fig:0}(a)
we plot $F^D(t)$ %defined in Eq.~\ref{eq:drive}.
as a function of time with
%The time independent
constants $F^{dc}=0.1$, 
$F^{ac}=0.05$ and $f=0.01$ cycles per time unit $\tau$.
The temporal period of the driving force is
$T = 1/f = 100 \tau$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%RAMP
%To avoid transient oscillations at early times, the dc driving force is initially zero and slowly increased %$F^{dc}$. at a rate of $\Delta F^{dc} = 0.01$ every $\Delta t = 4$ time units  to the constant value $F^{dc}=0.1$. In Fig.~\ref{fig:0}(a) we plot $F^{dc}$ in blue to show the increase in  $F^{dc}$ for the first $40$ time units In orange we show  the combined ac and dc drive $F^D(t)$ when the magnitude of the ac applied force is initially zero.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%since $\sin{(0)}=0$.
We mark the maxima of $F^{ac}(t)$
with the
vertical dashed lines %in panels (a) and (b)
-- i.e. $\sin{(\omega t)} = 1$.
%
%
%with the initial driving force at is minimum value 
%$F^D(0) = F^{dc}$. 
%
In Fig.~\ref{fig:0}(b) 
we show the $y-$position of the particle
as a function of time.
We 
normalize $y$ by $\lambda$ %, the spatial period of the potential
to show  particle motion between substrate minima.  
The initial particle position is $y = 0 $. %1 a_0$,
%where the $F^l$ is negative.
%JUST BECAUSE
%causing the particle to move to
%a landscape minima at the start of the simulation.
As the driving force increases,
%the effects of the landscape become less obvious,
the motion of the particle
synchronizes with the driving period $T$.
We measure 
average particle velocity $\langle{v}_y\rangle$
as the displacement %$\Delta y = y(t_0+T) - y(t_0)$
over the period of the driving force.
The particle moves
in the positive y-direction
through $\Delta y = 2 \lambda$ over the time period $T$,
with 
the average velocity 
$\langle {v}_y \rangle= 2 \lambda f$. % where $T = 1/f$.
[TODO: update description!]
The horizontal dashed lines
coincide with the condition the particle is at a substrate minima
where substrate force  $F^l = -A_p$,  
i.e. $\sin{(\pi y / \lambda)} = 1$.
 %or $\pi y / \lambda = m \pi/2$, where $m = 1, 5, 7$, {\it etc.}
%Once the particle motion
%coincides with the applied drive,
%indicating synchronization,
The particle synchronizes its motion such that the 
edriving force is maximum when the landscape 
force is minimum,
as indicated %with the coincidence of 
with the intersection of
vertical and horizontal lines.  
%i.e. the particle position $y/\lambda$.  
The slope of $y/\lambda$
is proportional to the net force on the particle.
This can be seen in 
Fig.~\ref{fig:0} %we demonstrate this relationship,
where local extrema appear in $y/\lambda$
when $F_{D}(t) \approx 0 $. 
\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{fig2.pdf}
\caption{(a) The applied driving force $F^D(t)$. % (Eq.~\ref{eq:drive}).
  %where the parameter $F^{dc}$ (blue) is slowly increased from zero %to a constant value %as described in the text.
  (b) 
  The $y-$position of the driven particle
  %of a single driven particle
  normalized by the period of the substrate $\lambda$.
  %as a function of time
  }
\label{fig:0}
\end{figure}
\end{center}

{\it NOTE: YOUR $A_P$ VALUES ARE TOO SMALL TO MAKE THIS A MEANINGFUL PHASE VARIALBE.  YOU NEED TO SCALE WITH THE DRIVE FORCE AMPLITUDES.  THIS CAN ALSO HELP YOU UNDERSTAND WHY YOU ARE GETTING BIG JUMPS IN POSITION COMPARED TO JUNIPER ET AL.  YOU ARE WORKING IN THE WEAK SUBSTRATE LIMIT.  also insert plots of $y/\lambda$ over a single period with the phase plots - like juniper}
  It is useful to compare
  mode-locked quantities %periodic signals
  in a two dimensional phase plot
  to distinguish fully and partially synchronized
  behavior.  
  In a non-driven system, an appropriate
  phase space is particle velocity $v_y$ versus position $y$.  
  In a system driven parallel to the $y-$direction,
  %the particle velocity and position increase
  %in time. % due to $F^{dc}$.
  %Since a system does not form
  %a closed loop in
  %$v_y$ vs $y$ space,
  we define phase variables 
  to account for the net increase in velocity
  and position.
  The phase position is
  defined as 
  %within the substrate period as 
  %We define a phase variable 
  \begin{equation}
    %(y mod \lambda) / \lambda
    \phi(t) = 2\pi(y(t)-\langle v_y \rangle t)/\lambda
  \end{equation}
  centered about the average particle velocity $\langle v_y \rangle$
  and normalized by the substrate period $\lambda$ \cite{Juniper2015}.
  In phase diagrams we plot $\phi(t)$ %phase
  versus the phase velocity 
  \begin{equation}
    %(y mod \lambda) / \lambda
    \dot{\phi}(t) = 2\pi(v_y(t)-\langle v_y \rangle /\lambda.
  \end{equation}
  %Juniper %REF 53
  %and easily generated with a computer code 
  %or oscilloscope \cite{Tong1997}.
  When velocity
  is mode-locked to %repeat periodically
  a spatial location
  a closed loop appears in  
  phase space. % showing the relationship
  %between two periodic functions
  The pattern is determined by the mode,
  or frequency ratio,
  so a 1:1 mode appears as a circle or oval.
  Nodes appear in the oval 
  for higher modes,
  sometimes forming figure-eights
  or other recognizable patterns.
  A system that is not fully phase locked
  will apppear as an unclosed loop.
  Such quasiperiodic systems are
  not fully synchronized.
  %and the shifts in phase space represent
  %small changes in system behavior.
  With a long simulation time,
  a quasiperiodic phase diagram
  fills the plotting region due to the gradual shift
  in the velocity-position relationship.
  %with a frequency generator,
  %where two combined frequencies at perpendicular orientations
  %\footnote{The term phase
  %has two scientific meanings:  
  %oscillation phase $\phi_0$ is the constant of the argument
  %in a periodic function
  %$\sin{(\omega t + \phi_0)}$ and phase space is
  %used to characterize oscillating systems with
  %parametric plots.}.

  %OKAY, WHY AREN'T MY AMPLITIDES \phi \pm 2\pi and \dot{\phi} \pm 4\pi.
  In Fig.~\ref{fig:phase}
  we plot $\dot{\phi}(t)$ versus $\phi(t)$
  for increasing substrate amplitude $A_p$.
  We fix the driving force with parameters
  $F^{dc} = 0.1$ and frequency $f = 0.01$ and $F^{ac} = 0.2$.
  In Fig.~\ref{fig:phase}(a)
  there is no substrate ($A_p = 0.0$)
  and the phase plot is a closed oval
  centered at
  $(\phi,\dot{\phi})=(10,0)$
  with a semimajor axis of $\Delta \phi = 20$ %ANALYTIC
  and semiminor axis of $\Delta \dot{\phi} = 2\pi v_{max} /\lambda$.
  [insert analysis.]
  As the force from the substrate
  increases,
  nodes form in the phase diagram
  and the motion becomes quasiperiodic
  so the loops in phase space do not fully overlap.
  In Fig.~\ref{fig:phase}(b)
  $A_p = 0.05$
  the spatial properties are similar to
  those in $A_p = 0.0$
  with 
  $(\phi,\dot{\phi})=(10,0)$
  with a semimajor axis of $\Delta \phi = 20$.
  The dynamical properties
  are asymmetric,
  with three nodes in the positive $\dot{\phi}$ values.
  The thickening of the line
  indicates the system is not fully synchronized.
  [insert analysis.]
  As the substrate
  force becomes larger,
  $\phi$ shifts to lower values
  and $\dot{\phi}$ to positive values,
  indicating
  the particle can only move 
  backward over a short distance.
  In Fig.~\ref{fig:phase}(c)
  $A_p = 0.1$
  the phase properties are similar to
  those in $A_p = 0.05$,
  the three nodes have 
  increased asymmetry in both phase variables 
  $(\phi,\dot{\phi})$.
  The nodes deepen,
  indicating [insert analysis.].
  In Fig.~\ref{fig:phase}(d)
  $A_p = 0.2$
  the pattern shifts
  to two nodes,
  [indicating change analysis].
  In Fig.~\ref{fig:phase}(e)
  $A_p = 0.25$
  the system returns to a nodeless
  orbit,
  shaped like a triangle [because why?]
  In Fig.~\ref{fig:phase}(f)
  $A_p = 0.3$
  the particle is trapped between substrate minima,
  and traces out a small unclosed
  orbit in phase space [because...]
  The phase velocity is near zero
  throughout the motion -
  [comment on initial conditions]
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{phase.pdf}
      \caption{
        Phase plot of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0}.  $F^{ac} = 0.2$ and $A_p = $ (a) $0.0$, (b) $0.05$, (c) $0.1$, (d) $0.2$, (e) $0.25$ and (f) $0.3$.
      }
      \label{fig:phase}
    \end{figure}
  \end{center}

@@

  %Consider a non-zero temperature in the simulation.
  %in which particles will collide with invisible particles
  %making up the suspending fluid.
  In molecular dynamics simulations
  it is common to treat the 
  invisible fluid particles as a continuous substance
  to reduce computational expense.
  Temperature effects
  can be modeled by applying randomized forces $f^T$
  to the visible particles.
  %\footnote{%In our simulations %np.random.normal
  We use the normal distristribution from the NumPy random module
  to generate a series of $f^T_n$ values for
  each integer timestep $n$ \cite{numpy}.
  A normalized random distribution of forces
  causes fluctuations in %particles to emulate Brownian
  motion 
  equally in all
  directions such that the force $f^T$
  averaged over a finite time interval
  is zero.  In one dimension this is expressed as 
  \begin{equation}
    \langle f^T(t) \rangle = \frac{1}{N} \sum_n^N f^T_n = 0
  \end{equation}
  where $n$ is an integer indicating
  discrete simulation timesteps and 
  $t = N \Delta t$.
  %Random normal distributions are not correlated 
  %over the independent variable,
  %for the independent variable to be time
  %\begin{equation}
  %\langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)
  %\end{equation}
  %for times $t$ and $\tau$,
  %where $\delta(t-\tau)$ is the Dirac-delta function.
  %Here the scaling factor energy of 
  %$k_B T$ is
  %derived from the Boltzmann constant $k_B$
  %and temperature $T$ \cite{Allen2017}.
  A particle
  with sufficient energy $k_b T_{min}$ may 
  hop over landscape
  barriers.
  % (a) 
  In our simulations,
  we define temperature as 
  $k_b T/E_0 \rightarrow T$
  with constants set to unity
  to
  %In these units
  compare directly with force. 
  %in order to estimate the degree of random fluctuation.

  {\bf With no applied driving force,
    find 
  the minimum temperature required for a single particle
  to hop over maxima in the potential landscape.}
  %$T_{min} > A_p$.
  Assume the particle is confined to
  move along the $y-$direction,
  include Brownian motion 
  in the model.
  In Fig.~\ref{fig:brownian},
  we demonstrate the transition
  from pinned to hopping
  in 
  %Measure the position vs. time
  a non-driven colloid for $T/A_p = 4.0$, $5.0$, and $6.0$.
  The crossover
  to a hopping regime occurs at $T/A_p \approx 5.6$.
  %Reproduce these results.  
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{brownian_particle_dt0.1}.pdf}
      \caption{
        Motion of a particle undergoing Brownian motion
        on a washboard potential
        energy landscape.
        (a) $T/A_p = 4.0$ no hopping occurs.
        (b) $T/A_p = 5.0$ a three hops occur %at $t = 130000$
        across distances of $\Delta y = 2 \lambda$.
        (c) $T/A_p = 6.0$ many hops occur.
        Note the scale of the $y-$axis differs in each panel
        and the time scale is
        much greater than in Fig.~\ref{fig:0}.
      }
      \label{fig:brownian}
    \end{figure}
  \end{center}
  In Fig.~\ref{fig:brownian}
  we show the position versus time of a particle
  confined to a sinusoidal landscape
  undergoing Brownian motion.
  We increase the temperature relative
  to the amplitude of the landscape
  troughs until the particle enters a hopping regime.
  In  Fig.~\ref{fig:brownian}(a)
  the temperature is $T/A_p = 4.0$.
  The particle executes a 
  random walk centered at the potential minima $y/\lambda = 10$.
  We ran many simulations and never observed a hop to another minima
  within this simulation time.  
  In  Fig.~\ref{fig:brownian}(b)
  $T/A_p = 5.0$,  hops between
  potential minima are possible but not probable,
  a back-forth hop occurs from
  $y/\lambda = 10$ to $12$ at
  $t \sim 40000 \tau$ and a single hop from 
  $y/\lambda = 10$ to $8$ occurs at
  $t \sim 280000 \tau$.
  In other simulations with identical parameters,
  we sometimes observed no hops or two hops between minima,
  as expected with random fluctuating systems.
  In  Fig.~\ref{fig:brownian}(c)
  $T/A_p = 6.0$ 
  we observe many hops.
  The random thermalized kicks are
  sufficiently large to make the particle perform
  what appears to be 
  a random walk of hops atop the substrate.
  [prove it]
  %in addition to the small scale random walk executed
  %by all particles in this section.
